### 2023-04-06 chapter2/chapter2.tex
Added substitution figure to chapter 2

\section{Results}
Here's where my results will go!

@@

\subsection{Fitting substitution models}
To fit amino acid substitution matrices to disorder and order regions, 25 meta-alignments were constructed by randomly sampling 100,000 columns from the respective subsets in the filtered regions derived from the 30 residue length cutoff. To determine the effect of gaps, the maximum fraction of gaps was set at 0, 50, 100\%. The combination of the region types and sampling strategy yielded six different sets of meta-alignments. A GTR20 substitution model with four FreeRate categories and optimized state frequencies was fit to each meta-alignment using IQ-TREE 1.6.12~\cite{Nguyen2014}. Exchangeability and rate coefficients were normalized to make the average rate of each model equal to 1. All figures are derived from the maximum 50\% gap fraction meta-alignment set unless otherwise noted.

>>>>

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/substitution.png}
\centering
\caption{\textbf{Amino acid substitution models fit to disorder and order regions.}
\textbf{(A)} Amino acid state frequencies of substitution models. Amino acid symbols are ordered by their enrichment in disorder regions, calculated as the disorder-to-order ratio of their frequencies. Error bars represent standard deviations over models fit to different meta-alignments ($n = 25$). \textbf{(B)} $\log_{10}$ disorder-to-order ratios of exchangeability coefficients. \textbf{(C)} $\log_{10}$ disorder-to-order ratios of rate coefficients. The vertical and horizontal axes indicate the initial and target amino acids, respectively.}
\label{fig:substitution}
\end{figure}

@@

\subsection{Fitting amino substitution models}
To fit amino acid substitution matrices to disorder and order regions, 25 meta-alignments were constructed by randomly sampling 100,000 columns from the respective subsets in the filtered regions derived from the 30 residue length cutoff. To determine the effect of gaps, the maximum fraction of gaps was set at 0, 50, 100\%. The combination of the region types and sampling strategy yielded six different sets of meta-alignments. A GTR20 substitution model with four FreeRate categories and optimized state frequencies was fit to each meta-alignment using IQ-TREE 1.6.12~\cite{Nguyen2014}. Exchangeability and rate coefficients were normalized to make the average rate of each model equal to 1. All figures are derived from the maximum 50\% gap fraction meta-alignment set unless otherwise noted.
